The Hosting Environment of the Advanced Resource Connector middleware

### 2008-08-04 doc/hed/ARCHED_article.tex
Extending introduction of HED document by adding some design ideas - everybody is welcome to add own.

@@

>>>>

Whole design of the HED is built around idea of flexibility and modularity. Inside HED developer or deployer is supposed to use only as much as needed. This is why the HED mostly consists of pluggable modules with some glue between them.

Because in it's current state it mostly provides modules for building SOAP based Web Services there is common misunderstanding that HED is just yet another implementation of Web Services development framework like Axis, gSOAP, XFire or any other of numerous implementations. But instead the idea of HED is to provide framework for gluing functionalities and not a re-implementation of various standards. Effectively that means if Apache 2 web server is considered by developers as necessary for serving as frontend to services there could be plugin written which puts Apache 2 into a chain of other plugins of the HED.

In current implementation you will not find Apache or Axis plugins. That is because developers of HED were concerned very much about lightweigtness of solution and needed rather simple and light despite simplified implementation of supported protocols. As result some basic things like SOAP and HTTP are implemented inside HED. While external software is used whenever that is found to be appropriate - like in case of TLS, (Grid)FTP, LDAP and some other features. That does not exclude possibility to have plugins using entirely external solutions either developed or accepted from third parties.

The HED is relatively young framework and there are quite many rough corners and non-flexible solutions. The situation will hopefully improve with time. We would be grateful for any suggestions how to improve architecture and code of the HED. Statements like "you are doing crap, i'll better use Axis" are understood but not welcome and are usually reacted adequately.

@@

\subsubsection{PDC}

\subsubsection{Security Handlers}
